\documentclass{article}

\usepackage[preprint]{neurips_2024}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{url}
\usepackage{booktabs}
\usepackage{amsfonts}
\usepackage{nicefrac}
\usepackage{microtype}
\usepackage{xcolor}

\title{Differential Privacy in Image Classification using ResNet-20 and DP-SGD Optimization}

\author{
    Praveen Rangavajhula\\
    Department of Computer Science\\
    University of Georgia\\
    Athens, GA, 30602\\
    \texttt{praveen.rangavajhula@uga.edu} \\
    \And
    Alexander Darwiche\\
    Department of Computer Science\\
    University of Georgia\\
    Athens, GA, 30605 \\
    \texttt{alexander.darwiche@uga.edu} \\
    \And
    Deven Allen\\
    Department of Computer Science\\
    University of Georgia\\
    Athens, GA, 30605 \\
    \texttt{dca09692@uga.edu} \\
}

\begin{document}

    \maketitle

    \begin{abstract}

        This project proposes a differentially private image classification system using ResNet-20 with various
        optimizers, starting with Differentially Private Stochastic Gradient Descent (DP-SGD) as a baseline.
        We aim to make incremental improvements with additional optimization techniques, exploring both non-private
        and DP versions of optimizers, and justifying our choices based on prior work and their potential
        to outperform others.
        The project will focus on achieving competitive accuracy while satisfying privacy guarantees.
        Additionally, we are investigating ways to enhance accuracy by modifying optimizer components,
        such as gradient clipping (potentially using techniques like automatic clipping), and exploring
        possible improvements in noise management.

    \end{abstract}


    \section{Introduction}\label{sec:introduction}

    The increase in productivity of machine learning models, especially in image classification, has raised concerns over privacy. 
    Differential privacy (DP) specifically addresses these concerns by ensuring that models do not inadvertently leak sensitive 
    information about individual data points. 
    In this proposal, we focus on the ResNet-20 model, which is well-suited for datasets like CIFAR-10~\cite{Idelbayev_ResNet20}, 
    and aim to implement and improve DP-SGD for achieving better privacy guarantees without significantly compromising accuracy.


    \section{Motivation and Problem Statement}\label{sec:motivation-and-problem-statement}
    In many real-world applications, such as healthcare and finance, privacy concerns hinder the deployment of machine
    learning models.
    Current state-of-the-art models like ResNet-20 achieve high accuracy but are vulnerable to attacks that could leak 
    sensitive information. 
    An example of a differentially private optimizer is Differentially Private Stochastic Gradient Descent (DP-SGD), which has been shown
    to effectively reduce privacy leaks, but has challenges in balancing model accuracy and privacy~\cite{Abadi_2016_DeepLearningDifferentialPrivacy}.
    By incorporating differential privacy techniques through the use of DP-SGD, we aim to develop a balanced model that acheives both high accuracy 
    and strong privacy guarantees.



    \section{Methodology}\label{sec:methodology}

    \subsection{Model Architecture: ResNet-20}\label{subsec:model-architecture:-resnet-20}


    We propose utilizing the ResNet-20 model~\cite{Idelbayev_ResNet20} for CIFAR-10,
    a standard dataset for image classification tasks.
    We selected a 20-layer ResNet for its deep architecture and strength in image classification problems~\cite{DBLP:journals/corr/HeZRS15}.
    20
    layers should be enough depth to adequately model many features, while not encountering the higher training error encountered
    with excessively \("\)deep\("\) architectures. \cite{DBLP:journals/corr/HeZRS15}

    If necessary, we may modify the architecture slightly to optimize for DP compatibility.

    \subsection{Non-private Optimizers to Try}\label{subsec:non-private-optimizers-to-try}
    We propose implementing 4 non-private optimizers to establish baseline performance for ResNet-20 on CIFAR-10.
    Three of these optimizers will be First-Order optimizers
    that all build on one another.
    The last optimizer that we will explore is a Second-Order optimization technique known as Cubic .

    \begin{itemize}
        \item \textbf{SGD:} Standard Stochastic Gradient Descent for baseline comparison.
        This optimizer works by calculating the gradient over a minibatch
        and updating the model parameters with the following update rule: $\theta + \eta * \Delta g$, where $\theta$ is model parameters, $\eta$ is
        the learning rate, and $\Delta g$ is the gradient for that minibatch~\cite{papernot2022hyperparametertuningrenyidifferential}.
        \item \textbf{RMSprop:} Root Mean Square Propagation (RMSprop) builds on SGD by including the a \("\)moving average\("\) factor.
        This factor functions by scaling the gradient
        each step, based on the gradient of the previous data points.
        This is done by dividing the gradient, at each model parameter update,
        by the moving average squared gradient: $(\Delta g_{t-1}^{2} * (1-\delta) + \Delta g{t}^{2}*\delta)^{\frac{1}{2}}$,
        where $\Delta g_{t-1}^{2}$ is the squared gradient average from the previous step, $\Delta g_{t}^{2}$ is
        the squared gradient of the current step, and $\delta$ is the \("\)moving average\("\) factor~\cite{DBLP:journals/corr/abs-1807-06766,Jason_Huang_2020}.
        \item \textbf{ADAM:} Adaptive Moment Estimation (ADAM) further build on RMSprop by including another \("\)moving average\("\) factor, this time for the gradient. In the general gradient update rule formula, instead of gradient,
        ADAM substitutes in the gradient moving average: $m_{t} = \Delta g_{t-1} * (1-\delta) + \Delta g{t}*\delta$~\cite{DBLP:journals/corr/abs-1807-06766}.
    \end{itemize}

    \subsection{Differentially Private Optimizer: DP-SGD}\label{subsec:differentially-private-optimizer:-dp-sgd}
    We propose implementing DP-SGD as our privacy-preserving algorithm.
    The key components of DP-SGD are:
    \begin{itemize}
        \item \textbf{Gradient Clipping:} Limits the influence of individual examples during training.
        \item \textbf{Noise Addition:} Adds noise to gradients to ensure privacy (via Opacus or TensorFlow Privacy libraries).
        \item \textbf{Privacy Accounting:} We will use Rényi Differential Privacy (RDP) for privacy budget tracking.
    \end{itemize}

    \subsection{Incremental Improvements}\label{subsec:incremental-improvements}
    After we have privatized SGD, we propose making the following enhancements:
    \begin{itemize}
        \item Adding an adaptive learning rate by incorporating the Moving Average of Gradients Squared (RMSprop)~\cite{DBLP:journals/corr/abs-1807-06766}
        \item Adding a moving average for gradient (ADAM)~\cite{DBLP:journals/corr/abs-1807-06766}
        \item Alternative noise mechanisms and their effect on utility-privacy tradeoffs. [NEED JUSTIFICATION]
        \item Adaptive gradient clipping methods that dynamically adjust the clipping threshold. [NEED JUSTIFICATION]
    \end{itemize}

    \subsection{Rationale for Choosing DP-SGD}\label{subsec:rationale-for-choosing-dp-sgd}
    \begin{itemize}
        \item provides well-documented privacy guarantees~\cite{Abadi_2016_DeepLearningDifferentialPrivacy}
        while maintaining decent utility for image classification tasks.
        \item The addition of noise and gradient clipping help ensure $(\epsilon, \delta)$-differential privacy,
        making it ideal for sensitive applications.
        \item Previous work shows that DP-SGD, when optimized, can yield near state-of-the-art accuracy
        for differentially private models~\cite{De_2022_ScaleDP_ImageClassification}.
    \end{itemize}

    \subsection{Why This Approach Will Outperform Others}\label{subsec:why-this-approach-will-outperform-others}
    \begin{itemize}
        \item Our approach leverages the simplicity of ResNet-20, optimized for smaller datasets like CIFAR-10,
        combined with DP-SGD, a proven differential privacy technique.
        \item By experimenting with different gradient clipping techniques and noise scales,
        we aim to find an optimal trade-off between accuracy and privacy.
        \item We will investigate modifications like adaptive clipping to enhance performance.
    \end{itemize}

    \subsection{Pseudocode for Non-Private SGD}\label{subsec:pseudo-code-for-non-private-sgd}
    Below is a simplified pseudocode for the non-private SGD we plan to privatize:
    \begin{verbatim}
        for each batch (X, y):
            pred = model(X)
            loss = loss_fn(pred, y)
            loss.backward()
            optimizer.step()
            optimizer.zero_grad()
    \end{verbatim}


    \section{Experimental Setup}\label{sec:experimental-setup}

    \subsection{System Description}\label{subsec:system-description}
    We will use PyTorch~\cite{pytorch_2019} for model implementation and training.
    The DP-SGD~\cite{Abadi_2016_DeepLearningDifferentialPrivacy} implementation will be based on the Opacus library~\cite{opacus}.
    Training will be performed on GPUs available via our departmental server csci-cuda.cs.uga.edu.

    \subsection{Dataset}\label{subsec:dataset}
    We will use the CIFAR-10 dataset~\cite{cifar10_dataset}, consisting of 60,000 32x32 RGB images, which is commonly used for
    image classification tasks.
    The dataset is built-in in PyTorch~\cite{pytorch_2019}, and we will load it using standard libraries.

    \subsection{Metrics}\label{subsec:metrics}
    \begin{itemize}
        \item \textbf{Training Loss/Accuracy:} Standard accuracy and training loss on CIFAR-10~\cite{cifar10_dataset}.
        \item \textbf{Privacy Budget:} We will measure $(\epsilon, \delta)$ using RDP~\cite{Mironov_2017_RenyiDP} to ensure privacy compliance.
        \item \textbf{Efficiency:} Time complexity and memory usage will be tracked.
    \end{itemize}

    \subsection{Baseline Models}\label{subsec:baseline-models}
    We will compare the performance of our modified differentially private models with standard private optimizers,
    including vanilla DP-SGD~\cite{Abadi_2016_DeepLearningDifferentialPrivacy}, DP-Adam,
    and DP-RMSprop~\cite{zhou_2020_private_adaptive_algorithms}.
    Additionally, we will benchmark against AdaClip~\cite{adaClip_2019} to evaluate the effectiveness of our automatic
    clipping and noise mechanism modifications.


    \section{Related Work}\label{sec:related-work}
    Several approaches to differentially private deep learning have been explored in the literature.
    \cite{Abadi_2016_DeepLearningDifferentialPrivacy} introduced DP-SGD, which has become a foundational technique for
    privacy-preserving model training.
    Our focus is on making incremental improvements to this framework by adapting it to DP-Adam and DP-RMSprop.
    Additionally, we aim to incorporate automatic clipping~\cite{bu2023automaticclippingdifferentiallyprivate}
    and explore modifications to the noise mechanism to enhance performance while maintaining privacy.


    \section{Timeline and Milestones}\label{sec:timeline-and-milestones}
    \begin{itemize}
        \item October 4, 2024: Best Accuracy Report 1 Due.
        \item October 18, 2024: Interim Report Due.
        \item November 8, 2024: Best Accuracy Report 2 Due.
        \item November 22, 2024: Final Report Due.
    \end{itemize}


    \section{Conclusion}\label{sec:conclusion}
    Through this proposal, we aim to develop a differentially private deep learning model that achieves strong
    privacy guarantees while enhancing the performance of existing techniques.
    We will use DP-SGD as a baseline and investigate adaptations to DP-Adam and DP-RMSprop.
    Our focus will be on incremental improvements, including the integration of automatic clipping and possibly
    modifications to the noise mechanism, to achieve competitive accuracy on CIFAR-10 while ensuring
    robust privacy protection.


    \bibliographystyle{plain}
    \bibliography{references}


    \section*{GitHub Contributions}
    The code and related materials for this project are available at our GitHub repository:
    \url{https://github.com/CS8960-Privacy-Preserving-Data-Analysis/final-project}.
    Contributions, issues, and discussions are welcome.


\end{document}
